DNSKEY Management

### 2012-12-10 paper/paper.tex
Chang to en_GB

\subsubsection{Single administrative domain}
Basically, once an organization has its main domain signed, it is relatively easy for any sub-entity within said organization to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.

@@

\paragraph{Penetration} SWITCH states on their website that as of
30. September 2012, 1'734'170 child-zones of \verb|ch.| have been
registered\footnote{\url{https://www.nic.ch/reg/cm/wcm-page/statistics/index.html}}. Upon
inquiry, SWITCH stated that there are around 370 secure delegations
from the \verb|ch.| zone. This is less than $0.02\%$ penetration
rate.

>>>>

\subsubsection{Single administrative domain}
Basically, once an organisation has its main domain signed, it is relatively easy for any sub-entity within said organisation to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organisation.

@@

\paragraph{Penetration} SWITCH states on their website that as of
30. September 2012, 1'734'170 child-zones of \verb|ch.| have been
registered\footnote{\url{https://www.nic.ch/reg/cm/wcm-page/statistics/index.html}}. Upon
enquiry, SWITCH stated that there are around 370 secure delegations
from the \verb|ch.| zone. This is less than $0.02\%$ penetration
rate.
